---
title: "Stock project"
format: pdf
editor: visual
---

## Stock Data

Download Data

CFG \<- Citizens Financial Group

GS-PJ \<- Goldman Sachs

MA \<- Mastercard

MS-PF \<- Morgan Stanley

Stocks can be categorized as high or low volume based on their trading activity. High and low refer to the maximum and minimum prices in a given time period. Open and close are the prices at which a stock began and ended trading in the same period. Volume represent the number of shares traded. The adjusted close is the closing price after adjustment for all applicable splits and dividend distributions.

```{r}
#Load the Data
CFGdata <- read.csv(file = "CFGstockdata(filtered).csv") 
GSPJdata <- read.csv(file = "GS-PJstockdata(filtered).csv")
MAdata <- read.csv(file = "MAstockdata(filtered).csv")
MSPFdata <- read.csv(file = "MS-PFstockdata(filtered).csv")

```

```{r}
# I would like to see open and close prices of the stock (the evolution)
#CFG Data
library(dplyr)
library(ggplot2)
library(lubridate)
#First convert them to Date:
CFGdata$Date <- format(CFGdata$Date, format = "%m/%d/%Y")
#Sort from the least recent to most recent
CFGdata <-CFGdata[order(as.Date(CFGdata$Date, format="%m/%d/%Y")),]
CFGdata$Date <- as.Date(CFGdata$Date, format = "%m/%d/%Y")
#Let's group per month and get the average
CFGdata %>%
  filter(Date < "2021-02-02") -> CFGdata2
mean(CFGdata2$High) -> AvgJan 
mean(CFGdata2$Low) -> AvglowJan
mean(CFGdata2$Open) -> AvgOpenJan
mean(CFGdata2$Close) -> AvgClsJan

CFGdata %>%
  filter(between(Date, as.Date("2021-02-02"), as.Date("2021-02-12"))) -> CFGdata3
mean(CFGdata3$High) -> AvgFeb
mean(CFGdata3$Low) -> AvglowFeb
mean(CFGdata3$Open) -> AvgOpenFeb
mean(CFGdata3$Close) -> AvgClsFeb

CFGdata %>%
  filter(between(Date, as.Date("2021-03-02"), as.Date("2021-03-12"))) -> CFGdata4
mean(CFGdata4$High) -> AvgMar
mean(CFGdata4$Low) -> AvglowMar
mean(CFGdata4$Open) -> AvgOpenMar
mean(CFGdata4$Close) -> AvgClsMar

CFGdata %>%
  filter(between(Date, as.Date("2021-04-01"), as.Date("2021-04-11"))) -> CFGdata5
mean(CFGdata5$High) -> AvgApr
mean(CFGdata5$Low) -> AvglowApr
mean(CFGdata5$Open) -> AvgOpenApr
mean(CFGdata5$Close) -> AvgClsApr

CFGdata %>%
  filter(between(Date, as.Date("2021-05-01"), as.Date("2021-05-11"))) -> CFGdata6
mean(CFGdata6$High) -> AvgMay
mean(CFGdata6$Low) -> AvglowMay
mean(CFGdata6$Open) -> AvgOpenMay
mean(CFGdata6$Close) -> AvgClsMay

CFGdata %>%
  filter(between(Date, as.Date("2021-06-01"), as.Date("2021-06-12"))) -> CFGdata7
mean(CFGdata7$High) -> AvgJun
mean(CFGdata7$Low) -> AvglowJun
mean(CFGdata7$Open) -> AvgOpenJun
mean(CFGdata7$Close) -> AvgClsJun

CFGdata %>%
  filter(between(Date, as.Date("2021-07-01"), as.Date("2021-07-12"))) -> CFGdata8
mean(CFGdata8$High) -> AvgJul
mean(CFGdata8$Low) -> AvglowJul
mean(CFGdata8$Open) -> AvgOpenJul
mean(CFGdata8$Close) -> AvgClsJul

CFGdata %>%
  filter(between(Date, as.Date("2021-08-01"), as.Date("2021-08-12"))) -> CFGdata9
mean(CFGdata9$High) -> AvgAug
mean(CFGdata9$Low) -> AvglowAug
mean(CFGdata9$Open) -> AvgOpenAug
mean(CFGdata9$Close) -> AvgClsAug

CFGdata %>%
  filter(between(Date, as.Date("2021-09-02"), as.Date("2021-09-12"))) -> CFGdata10
mean(CFGdata10$High) -> AvgSep
mean(CFGdata10$Low) -> AvglowSep
mean(CFGdata10$Open) -> AvgOpenSep
mean(CFGdata10$Close) -> AvgClsSep

CFGdata %>%
  filter(between(Date, as.Date("2021-10-02"), as.Date("2021-10-12"))) -> CFGdata11
mean(CFGdata11$High) -> AvgOct
mean(CFGdata11$Low) -> AvglowOct
mean(CFGdata11$Open) -> AvgOpenOct
mean(CFGdata11$Close) -> AvgClsOct

CFGdata %>%
  filter(between(Date, as.Date("2021-11-01"), as.Date("2021-11-11"))) -> CFGdata12
mean(CFGdata12$High) -> AvgNov
mean(CFGdata12$Low) -> AvglowNov
mean(CFGdata12$Open) -> AvgOpenNov
mean(CFGdata12$Close) -> AvgClsNov

CFGdata %>%
  filter(between(Date, as.Date("2021-12-01"), as.Date("2021-12-11"))) -> CFGdata13
mean(CFGdata13$High) -> AvgDec
mean(CFGdata13$Low) -> AvglowDec
mean(CFGdata13$Open) -> AvgOpenDec
mean(CFGdata13$Close) -> AvgClsDec


#Create a dataframe with the average value per month
df <- data.frame (AvgHigh  = c(AvgJan, AvgFeb, AvgMar, AvgApr, AvgMay, AvgJun, AvgJul, AvgAug, AvgSep, AvgOct, AvgNov, AvgDec),
                  Avglow = c(AvglowJan, AvglowFeb, AvglowMar, AvglowApr, AvglowMay, AvglowJun, AvglowJul, AvglowAug, AvglowSep, AvglowOct, AvglowNov, AvglowDec),
                  AvgOpn = c(AvgOpenJan, AvgOpenFeb, AvgOpenMar, AvgOpenApr, AvgOpenMay, AvgOpenJun, AvgOpenJul, AvgOpenAug, AvgOpenSep, AvgOpenOct, AvgOpenNov, AvgOpenDec),
                  AvgCls = c(AvgClsJan, AvgClsFeb, AvgClsMar, AvgClsApr, AvgClsMay, AvgClsJun, AvgClsJul, AvgClsAug, AvgClsSep, AvgClsOct, AvgClsNov, AvgClsDec),
                  Month = c("Jan", "Feb", "March", "April", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"))

#Create the time series plot
ggplot(CFGdata,aes(x=Date)) +
  geom_line(aes(y=High),color="blue")
#Create barchart with added parameters
attach(mtcars)
par(mfrow=c(2,1))
barplot(df$AvgHigh,
main = "Avegare Highest Stock Value per month",
xlab = "Month",
ylab = "Stock Value",
names.arg = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "July", "Aug", "Sep", "Oct", "Nov", "Dec"),
col = "darkred",
horiz = FALSE)
barplot(df$Avglow,
main = "Avegare Lowest Stock Value per month",
xlab = "Month",
ylab = "Stock Value",
names.arg = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "July", "Aug", "Sep", "Oct", "Nov", "Dec"),
col = "pink",
horiz = FALSE)



layout(matrix(c(1,1,2,3), 2, 2, byrow = TRUE))
barplot(df$AvgOpn,
main = "Avegare Open Stock Value per month",
xlab = "Month",
ylab = "Stock Value",
names.arg = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "July", "Aug", "Sep", "Oct", "Nov", "Dec"),
col = "darkblue",
horiz = FALSE)
barplot(df$AvgCls,
main = "Avegare Close Stock Value per month",
xlab = "Month",
ylab = "Stock Value",
names.arg = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "July", "Aug", "Sep", "Oct", "Nov", "Dec"),
col = "red",
horiz = FALSE)
  



```
