---
title: "Stock project"
format: pdf
editor: visual
---

## Stock Data

Download Data

CFG \<- Citizens Financial Group

GS-PJ \<- Goldman Sachs

MA \<- Mastercard

MS-PF \<- Morgan Stanley

Stocks can be categorized as high or low volume based on their trading activity. High and low refer to the maximum and minimum prices in a given time period. Open and close are the prices at which a stock began and ended trading in the same period. Volume represent the number of shares traded. The adjusted close is the closing price after adjustment for all applicable splits and dividend distributions.

```{r}
#Load the Data
CFGdata <- read.csv(file = "CFGstockdata(filtered).csv") 
GSPJdata <- read.csv(file = "GS-PJstockdata(filtered).csv")
MAdata <- read.csv(file = "MAstockdata(filtered).csv")
MSPFdata <- read.csv(file = "MS-PFstockdata(filtered).csv")

```

```{r}
# I would like to see open and close prices of the stock (the evolution)
#CFG Data
View(CFGdata)
library(dplyr)
library(ggplot2)
#First convert them to Date:
CFGdata$Date <- format(CFGdata$Date, format = "%m/%d/%Y")
#Reduce the size of the dataset
CFGdata %>%
  filter(Date < "3/1/2022") -> CFGdata2 

ggplot(CFGdata2,aes(x=Date))+
  geom_line(aes(y=Low),color="blue")
  
  geom_line(aes(y=Open),color="red")+
  geom_line(aes(y=High),color="pink")+
  geom_line(aes(y=Close),color="green") 
  
barplot()

```
